\documentclass[a4paper,12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[mono=false]{libertine}
\usepackage[margin=1in]{geometry}
\usepackage[shortlabels]{enumitem}
\usepackage{hyperref}
\usepackage{xcolor,booktabs}

\date{}
\title{\textsc{Curriculum Vitae}}
\author{\emph{Herman Bergwerf}\\%
{\small \textsc{Contact:} \href{mailto:post@hbergwerf.nl}{post@hbergwerf.nl}}\\%
{\small
\href{https://www.hbergwerf.nl}{hbergwerf.nl}~|~\href{https://www.linkedin.com/in/hbergwerf/}{LinkedIn}~|~\href{https://github.com/bergwerf}{GitHub}
}}
\pagenumbering{gobble}

% Color of links.
\hypersetup{pdfborderstyle={/S/U/W 1},colorlinks,
  linkcolor=[HTML]{3366CC},
  citecolor=[HTML]{000000},
  urlcolor=[HTML]{3366CC}}

\begin{document}
\maketitle
\noindent
I am specialized in solving difficult logical problems and implementing the solutions in software. Visual communication plays a key role in many of my projects, and I enjoy designing beautiful and innovative interfaces. I like brainstorming together with a team to find the path towards a good product, and to make technical descisions that are future-proof.

\section*{Education}

\begin{figure}[h]
\centering
\begin{tabular}{lll}
\toprule
{\bf Degree} & {\bf Programme} & {\bf Institution}\\
\midrule
Bachelor & \emph{Nanobiology} & Delft University of Technology\\
Master & \emph{Mathematical Foundations of Computer Science} & Radboud University Nijmegen\\
\bottomrule
\end{tabular}
\end{figure}

\section*{Past Projects}

\begin{figure}[h]
\centering
\begin{tabular}{llll}
\toprule
{\bfseries Year} & {\bfseries Client \& Project} & {\bfseries Technologies}\\
\midrule
2022 & Omoda -- ML/AI for Image Processing & \emph{Python, MediaPipe, Tensorflow}\\
2017-21 & CreativeQuantum -- Chemical Diagrams & \emph{Dart, HTML Canvas}\\
2017 & Learnbeat -- Molecule Sketching for Education & \emph{JavaScript, NPM, HTML Canvas}\\
2016 & Profects -- Custom Mailing Scheduler & \emph{Golang, PostgreSQL, Docker}\\
\bottomrule
\end{tabular}
\end{figure}

\section*{Academic Work}

\begin{itemize}[--,labelsep=3mm,leftmargin=*]
\item \emph{An Exploration of Graph Pebbling} (2023)\\
Master's thesis supervised by Dr. Wieb Bosma. \textsc{\href{https://arxiv.org/abs/2303.04590}{doi: 10.48550/arXiv.2303.04590}}
\item \emph{Circular lists in Iris $\ast$ deduction rules of~\,$\triangleright$} (2022)\\
Research internship supervised by Dr. Robbert Krebbers. \textsc{\href{https://doi.org/10.5281/zenodo.6340500}{doi: 10.5281/zenodo.6340500}}
\item \emph{Nerve fiber tracing in bright-field images of human skin using deep learning} (2019)\\
Bachelor's thesis supervised by Dr. Erik Meijering. \textsc{\href{https://ieeexplore.ieee.org/document/8759504}{doi: 10.1109/isbi.2019.8759504}}
\end{itemize}

\end{document}